Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
Invert two paragraphs in Alectryon section as suggested by Jérémy.

The transition happened gradually, over a few weeks: for each snippet of \coq code that was in the book, we had to take the following steps:

>>>>

Once the infrastructure was in place, the transition happened gradually, over a few weeks: for each snippet of \coq code that was in the book, we had to take the following steps:
